Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-03-21 Writing/CEA_3rd_round/replies_rev.rmd
update manuscript, appendix and comments to the editor

We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version. This round of revision turned out to be much more importnat than the previous one. One of your comments was paritculary important, and we were able to correct our mistake before this paper is published. Thank you so much for making this article better toghether with us. We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well. Below, you find your comments in black and our replies in blue.

@@

We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version. One of your comments was particularity important and we were able to correct our mistake before this paper is published. So, thank you so much. We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well. Below, you find your comments in black and our replies in blue.

@@

<span style="color:blue">  
Please see Figure E.1 in Appendix E that shows the convergence of CNN for a single simulation round. We cannot show this kind of figure for all the simulation rounds. But, any interested readers can replicate our work as the codes will be accessible publicly. Please also see the figure below. CNN severely underestimates the impact of N and estimated yield response to N is almost flat, but not exactly flat. Please see the figure below showing some examples of yield response function estimated by CNN with "aabbyytt" modeling scenario. Each of the lines indicates yield response curve of a specific site.

@@

<span style="color:blue">  
Fiels studies were used to obtain the plausible range of optimal EONR and the size of error. 
</span>

@@

<span style="color:blue">  
Please see page 19, line 323 and 328 for the precise definition of the RMSE for yield and EONR predictions.
</span>

@@

We actually realized the results presented in Figure 6 (in the previous round) is completely invalid. As you pointed out the problem with the relationship presented in the figure is basically comparing apples and oranges: comparing across simulation rounds. Figure 8 plots RMSE of yield and EONR predictions by model and simulation round for several simulation rounds. Figure 6 in the previous round was basically mixing RMSE from all the simulation rounds and finding R^2 of the two relationshiop. That is why R^2 was extremely low. Therefore, we decided to remove the figure entirely. Also, we no longer claim that yield and EONR predictions are not correlated at all as we realized that it is false. Thank you so much for saving us from claiming the false statement.

However, please note that our claim that better yield prediction does "not necessarily" lead to higher profit remains intact. According to your suggestions, we provide much more in-depth discussions about why that is the case under section 4.2. As you suggested, models that can recover the "structure" of the yield response function will perform well in predicting EONR. However, you can predict yield levels at the observed rates (rates that are actually applied in the experiment) without recovering the structure of the yield response function well (predicting yield levels well for wrong reasons). The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary obejective of predicting yield levels well at the "observed" nitrogen rate for each site well. Please see our more detailed discussions on this matter in section 4.2.

We understand your suggestion of running simulations under different magnitude of erorr comes from your doubt about why yield and EONR prediction is not correlated. But, we conducted simulations with different degrees of error anyway. **The results are shown in Appendix**.

@@

<span style="color:blue">  
Please see Figure H.1 that plots true yields (without error, epsilon) against predicted yields by model (CF is not presented as it does not predict yield levels as discussed in the article) for a single simulation round. RMSE is presented in the figure as well. As we have 1000 simulations, it is simply infeasible to present figures like this for all the simulation rounds. But, this figure provides a better sense of the value of RMSE and how good the fit is. 
</span>

@@

Please see Figure F.1 for illustrations of how yield responds to N site-specifically for several sites within a field. Please note that Figure xxx (Figure 5) presents exactly the models' ability to predict the impact of N on yield at different treatments (lowest to the second lowest, second lowest to third lowest, etc). As you can see in the figure, RF underestimates the impact of N on yield severely, which leads to the underestimation of EONR. BRF suffers negative bias as well. On the contrary, CF does not suffer this bias. Of course, the worst of all is CNN, which thinks that the impact of N on yield is almost nascent as you can see in Figure 5. On top of negative bias RF and BRF suffer, their estimation of the impact of N is also less accurate than CF. That is why CF performs better than RF and BRF in profit. Please note that CF does not even estimate (3). It estimates the change in yield when N is increased from one rate to another rate as discussed in the paper.

@@

<span style="color:blue">  
Please see page xx, line xx for a new list of studies that attempt to estimate EONR. Please note that the previous stufies relevant to out study are those that apply ML methods to OFE data with the ultimate intention of estimating site-specific EONR. There is no study that tests the performance of EONR using real data. This is because that is fundamentally impossible as we mentioned above. There are studies that predict field-level (not site-specific within a field) EONR for individual fields one by one using a traditional regression approach, then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (Shun cite a paper that does this). But, please note that the field-level EONRs they compare against are "estimated." Why did they "estimate" EONR for each field? That is because they do not (and will never) know the true EONR for each field. Moreover, the objective of such studies are fundamentally different from ours. Our focus is on site-specific EONR within a field, theirs' are on field-specific EONR. We consider those studies not very relevant. We believe including those studies will simply bloat the introduction. 
</span>

@@

<span style="color:blue">  
We already discuss our results to the state of the art of the literature. The state of the art is sadly trying to predict yields site-specifically as well as possible. We show that such practice can be misleading and economically harmful when your ultimate goal is to actually help farmers make nitrogen application decisions (predicting EONR well). There is nothing wrong with our approach in yield prediction as evident in Figure 12. We are using ML methods that have been used in the literature of OFE for site-specific input management. Those studies were published very recently. We added our description about how the size of epsilon affects our results briefly at line xx, page yy. But, it is imporatnt to realize that all the models uses the same data in our study. That is, the models are competing against each other on the level ground. Changing the size of error has little effects on the comparative advantage of CF over other models much.

@@

>>>>

@@

We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version. This round of revision turned out to be much more important than the previous one. One of your comments was particularity important, and we were able to correct our mistake before this paper is published. Thank you so much for making this article better together with us. We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well. Below, you find your comments in black and our replies in blue.

<!-- We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version. One of your comments was particularity important and we were able to correct our mistake before this paper is published. So, thank you so much. We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well. Below, you find your comments in black and our replies in blue. -->

@@

<span style="color:blue">  
Please see Figure D.1 in Appendix D that shows the convergence of CNN for a single simulation round. We cannot show this kind of figure for all the simulation rounds. But, any interested readers can replicate our work as the codes will be accessible publicly. Please also see the figure below. CNN severely underestimates the impact of N and estimated yield response to N is almost flat, but not exactly flat. 
<!-- Please see the figure below showing some examples of yield response function estimated by CNN under "aabbyytt" modeling scenario. Each of the lines indicates yield response curve for different sites.
 -->

@@

<span style="color:blue">  
Fields studies were used to obtain the plausible range of optimal EONR and the size of error. 
</span>

@@

<span style="color:blue">  
Please see page 19, Eq. (7) and Eq. (8) for the precise definitions of the RMSE for yield and EONR predictions.
</span>

@@

We actually realized the results presented in Figure 6 (in the previous round) is completely invalid. As you pointed out the problem with the relationship presented in the figure is basically comparing apples and oranges: comparing across simulation rounds. Figure 8 plots RMSE of yield and EONR predictions by model and simulation round for several simulation rounds. Figure 6 in the previous round was basically mixing RMSE from all the simulation rounds and finding $R^2$ of the two relationship. That is why $R^2$ was extremely low. Therefore, we decided to remove the figure entirely. Also, we no longer claim that yield and EONR predictions are not correlated at all as we realized that it is false. Thank you so much for saving us from claiming the false statement.

However, please note that our claim that better yield prediction does "not necessarily" lead to higher profit remains intact. According to your suggestions, we provide much more in-depth discussions about why that is the case under section 4.2. As you suggested, models that can recover the "structure" of the yield response function will perform well in predicting EONR. However, you can predict yield levels at the observed rates (rates that are actually applied in the experiment) without recovering the structure of the yield response function well (predicting yield levels well for wrong reasons). The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary objective of predicting yield levels well at the "observed" nitrogen rate for each site well. Please see our more detailed discussions on this matter in section 4.2.

We understand your suggestion of running simulations under different magnitude of error comes from your doubt about why yield and EONR prediction is not correlated. But, we conducted simulations with different degrees of error anyway. **The results are shown in Appendix G**.

@@

<span style="color:blue">  
Please see Figure E.1 that plots true yields (without error, epsilon) against predicted yields by model (CF is not presented as it does not predict yield levels as discussed in the article) for a single simulation round. RMSE is presented in the figure as well. As we have 1000 simulations, it is simply infeasible to present figures like this for all the simulation rounds. But, this figure provides a better sense of the value of RMSE and how good the fit is. 
</span>

@@

Please see Figure 2 for illustrations of how yield responds to N site-specifically for several sites within a field. Please note that Figure 6 presents exactly the models' ability to predict the impact of N on yield at different treatments (lowest to the second lowest, second lowest to third lowest, etc). As you can see in the figure, RF underestimates the impact of N on yield severely, which leads to the underestimation of EONR. BRF suffers negative bias as well. On the contrary, CF does not suffer this bias. Of course, the worst of all is CNN, which thinks that the impact of N on yield is almost nascent as you can see in Figure 5. On top of negative bias RF and BRF suffer, their estimation of the impact of N is also less accurate than CF. That is why CF performs better than RF and BRF in profit. Please note that CF does not even estimate Eq. (3). It estimates the change in yield when N is increased from one rate to another rate as discussed in the paper.

@@

Please see page xx, line xx for a new list of studies that attempt to estimate EONR. Please note that the previous studies relevant to our study are those that apply ML methods to OFE data with the ultimate intention of estimating site-specific EONR. There is no study that tests the performance of EONR using real data. This is because that is fundamentally impossible as we mentioned above. There are studies that predict field-level (not site-specific within a field) EONR for individual fields one by one using a traditional regression approach, then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (e.g., @Qin2018; @Ransom2019 @Wang2021; @wen2021machine). But, please note that the field-level EONRs they compare against are "estimated." Why did they "estimate" EONR for each field? That is because they do not (and will never) know the true EONR for each field. Moreover, the objective of such studies are fundamentally different from ours. Our focus is on site-specific EONR within a field, theirs' are on field-specific EONR. We consider those studies not very relevant. We believe including those studies will simply bloat the introduction.

@@

<span style="color:blue">  
We already discuss our results to the state of the art of the literature. The state of the art is sadly trying to predict yields site-specifically as well as possible. We show that such practice can be misleading and economically harmful when your ultimate goal is to actually help farmers make nitrogen application decisions (predicting EONR well). There is nothing wrong with our approach in yield prediction as evident in Figure E.1<!-- Figure 12 -->. We are using ML methods that have been used in the literature of OFE for site-specific input management. Those studies were published very recently. We added our description about how the size of epsilon affects our results briefly in Appendix G. But, it is important to realize that all the models uses the same data in our study. That is, the models are competing against each other on the level ground. Changing the size of error has little effects on the comparative advantage of CF over other models much.

@@

# References

<div id="refs"></div>

### 2022-03-21 Writing/manuscript_cea.rmd
update manuscript, appendix and comments to the editor

Information about crop yield response input management is critical for the identification of site-specific economically optimal input rates (EOIRs) [@bullock1998does], and the difficulty in estimating site-specific yield response functions accurately within a field is the primary explanation of the persistent relatively low the adoption rate of variable rate crop input application technology [@lowenberg2019setting]. Historically, site-specific yield response functions have been estimated using the data generated from strip trials conducted on only parts of fields [@makowski2001statistical; @scharf2002corn; @bullock2002adding; @mamo2003spatial; @hurley2004estimating; @anselin2004spatial; @scharf2005field; @ruffo2006site; @Miao2006; @puntel2019development].
But recently whole-field on-farm precision experimentation (OFPE) [@bullock2019] has allowed implementation of improved statistical experimental designs (e.g., Latin Square, Randomized Block) on entire fields [@laurent_kyveryga_makowski_miguez_2019; @licht_witt_2019]. Data generated from whole-field OFPEs typically have greater local variation in experimental input application rates and soil/field characteristics than do strip trial designs, which has improved the statistical identification of heterogeneous impacts of input management changes on yields. The resultant availability of more spatially detailed experiment data has encouraged a resurgence of interest in estimating site-specific yield response functions. For example, @barbosa2020modeling, @krause2020random and @Gardner21 used OFPE data to estimate site-specific yield response functions and economically optimal site-specific N fertilizer and/or seed rates. These recent studies used machine learning (ML) methods extensively in place of more traditional parametric modeling approaches. @barbosa2020modeling applied the Convolutional Neural Network approach, @krause2020random used Random Forest-based approaches, and @Gardner21 used the shape-constrained generalized additive model. 
But this trend of applying ML methods may raises concerns. Historically, agronomists have worked meticulously to develop clever experimental designs to identify causes of yield response to input management. But the aforementioned recent applications of ML methodologies pay little attention to identify such causes, instead attempting to validate their models by estimating yield prediction accuracy. But the ultimate goal of OFPE is the accurate prediction of EOIRs, not yields. These are distinct objectives, and achievement of one need not imply the other.

@@

Recent studies using ML methods to estimate the effectiveness of various agricultural input management strategies first estimate yield function, $f(I, \mathbf{c})$ (e.g., @krause2020random; @barbosa2020modeling; @Gardner21) and then derive changes in yield associated with changes in input rate to estimate site-specific input recommendations. On the other hand, Causal Forest is designed specifically to estimate a discrete version of Eq. \@ref(eq:eqn2) directly, examining the discrete changes in yield that result from discrete *changes* in the input application rate $I$, bypassing the estimation of $f(I, \mathbf{c})$. It may be suspected that CF will outperform other ML methods that identify EOIR indirectly through yield prediction. We now details how CF works below and why CF may perform better in predicting EOIR than other prediction-oriented ML methods used in the previous studies.

@@

The error term of the yield $\varepsilon$ represents the composite of all the unobserved factors that affect crop yield beyond $\alpha$, $\beta$, $ymax$ and $N$. Each cell $(i,j)$'s "true" optimal N application rate, denoted $N^{opt}_{i,j}$, was calculated by solving a profit maximization problem by cell assuming that the prices of corn and N fertilizer were $\$0.138/kg$ and $\$1.323/kg$, respectively. These prices are used consistently for our simulations. See Appendix C.1 for further details on how the paremeters were generated and sample maps of the parameters and true economically optimal N rates.

@@

Unlike RF, BRF, and CNN, CF estimates the impact of a binary treatment. In our context, CF estimates changes in yields (i.e., $\hat{\tau}_{N^{con} \rightarrow N^{tre}}(\mathbf{\Omega_{i}})$) caused by changes in N application rates from one experimental rate (control N rate, i.e., $N^{con}$) to another experimental rate (treatment N rate, i.e., $N^{tre}$). Since we have five N application rates, four "experiments" (treatments) are identified based on four ($N^{con}$, $N^{tre}$) combinations. A possible grouping to make such pairwise N application rate combinations, which we call the "CF-base," used $(N_1, N_2),(N_1, N_3),(N_1, N_4)$, and $(N_1, N_5)$. In this approach, the treatment effect is always estimated against the lowest N rate ($N_1$) as $N^{con}$. The `grf` package (version 1.2.0 [@tibshirani2018package]) in R was used for CF estimation. Just like RF and BRF, hyperparameters were tuned using cross-validatiaon.

@@

Interestingly, CNN completely failed in its estimations of site-specific EONRs. This happened because the site-specific yield response functions identified by CNN were linear, and all with the same slope. Therefore, CNN failed to capture a declining marginal product of N. The constant marginal product caused the estimated EONR to take on either the lowest or highest experimental N application rate. To examine whether this problem is a product solely of the specific choice of CNN architecture, we also tested another CNN model, which was analogous to CNN-ST proposed by @barbosa2020modeling. 
This architecture also estimated that yield and N rates were perfectly linearly related, and so estimated site-specific EONR poorly. Note that @barbosa2020modeling just compared models through the lens of yield prediction but did not use the estimated models to derive EONRs.

@@

Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions. It plots the estimated treatment effects against true treatment effects by treatment type and ML method under the "aabbyytt" scenario in one of the one thousand simulations rounds. First of all, CNN suffers from severe underestimation of the impact of N in this particular simulation round. RF also suffers from underestimation of the impact of N. Underestimation of the impact of N generally leads to the underestimation of EONR, which in turn results in profit loss. Underestimation bias from BF is not as severe as RF or CNN. However, unlike RF, BRF, and CNN, points for CF-base clustered around the red 1-to-1 line, meaning that the estimated treatment effects from CF did not exhibit significant bias in treatment effect estimation. Moreover, points are clustered more tightly about the 1-to-1 line for CF-base than BRF. That is, CF-base estimated treatment effects more efficiently than did BRF.

@@

Finally, the simulation results at a smaller and larger size of the error term are presented in Appendix xx as a sensitivity check for interested readers. Basically, qualitative results remain the same.

@@

Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations (see Figure \@ref(fig:vis-y-pred) in Appendix xx for example visualizations of predicted and true yields along with RMSE values by model). Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN. Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact along with the poor performance of RF in predicting EONR presented in \@ref(tab:table-optN) show that strong predictive power of yield levels does not imply accurate prediction of EONR. Further, RF shows vulnerability to the inclusion of many correlated variables, as is displayed for EONR prediction as well. While CNN performed worse than RF and BRF in "aby" and "abytt," it performed better than RF in more complicated modeling scenarios, showing robustness, at least in yield prediction, to inclusion of many correlated variables. Of course, while on average in the "aabbyy" and "aabbyytt" scenarios CNN predicted yields better than RF did, CNN's EONR predictions were worse than RF's, which further backs our claim that a good yield prediction capability does not imply good EONR prediction capability.

@@

Figure \@ref(fig:vis-MB-BRF-y) illustrates the distinction between yield prediction at observed points and yield response function prediction, giving insights into why good yield prediction does not necessarily lead to good EONR prediction in general. The black curves are the true yield response functions for two sites in a single simulation round. Red symbols represent true (circle) or predicted (triangle) yields at the rate observed in the data: the rate that was actually applied in the experiment. That is, 150 kg/ha was applied to the two sites in the experiment. Blue symbols represent true (circle) or predicted (triangle) yield at some rates that were not observed (or applied) for the two sites in the experiment. Prediciton-oriented ML methods train models to minimize errors in yield level prediction at the "observed" rates (red points). Both RF- and BRF-trained models predict yield level at the observed rate well for the two sites (the vertical distance between the red circle and triangle). However, as you move away from the observed N rate, yield prediction errors tend to become larger (of course smaller yield prediction erros can be observed at unobserved rates some times). More important, connecting the predicted yield points does not trace the true yield response curves well for both RF and BRF. Specifically, in this example, the predicted impact of N on yield from RF and BRF are both smaller than the true impact of N.

@@

In essence, Figure \@ref(fig:vis-MB-BRF-y) illustrats that good performance in predicinting yield "levels" at the "observed" points does not mean good performanc in predicting yield "response" function, which is about finding out what "would" happen to yield if rates other than the one actually applied were applied. This happens because you can predict yield "levels" for wrong reasons by giving wrong amount of credit to wrong drivers (variables) of yield levels. The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary obejective of predicting yield levels well at the "observed" nitrogen rate for each site well. This problem is also observable at Figure \@ref(fig:plot-tre), which shows both RF and BRF understimates the impact of N on yield: or in other words, their predicted site-speific yield response functions tend to be flatter than they truelly are. Of course, the CNN approach in our study is an extreme case where it completley fails to recognize the contribution of N on yield. But, remember that CNN does performs almost as good as RF and BRF in yield prediction as shown in Table \@ref(tab:table-y).

Since you need to be able to estimate yield curves (yield response function) well at the site level to predict site-specific EONR (not yield level) well, models' ability to predict yield levels well at the observed rates does not guarantee their ability to predict site-specific EONR well. In contrast to RF, BRF, and CNN, CF focuses to recover the yield response functions well (or alternatively the causal impact of N on yield at different discrete rates of N). We showed that CF can predict the impact of N on yield when N is chaned from an unobserved rate to another unobserved rats as shown in Figure \@ref(fig:plot-tre), which then translated to better performance in predicting EONR and profit.

All previous research has followed a two-step procedure to estimate site-specific EONRs. The first step was to select the model that predicts yield leves most accurately at the observed points, and the following step used the selected model to predict EONR. As discussed ealier, this practice can be economically harmful. Figure \@ref(fig:vis-RMSE-y-eonr) further illustrates the underlying problem. It plots RMSE of yield (x-axis) and EONR (y-axis) predictions by model and simulation round for several simulation rounds. As you can see clearly, the model with the lowest yield RMSE is not necessarily the model with the lower EONR RMSE for a given simulation round (simulation round xx and yy).

```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "The Relationship between Yield and EONR Prediction Performances under the aabbyytt scenario"}
vis_RMSE_y_eonr
```

@@

We examined the use of CF in the generation of site-specific input management recommendations. Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN. CF consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation. Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF. It is importnat to keep in mind that we are not claiming that CF always performs better economically than RF, BRF, and CNN. Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research.

>>>>

Information about crop yield response input management is critical for the identification of site-specific economically optimal input rates (EOIRs) [@bullock1998does], and the difficulty in estimating site-specific yield response functions accurately within a field is the primary explanation of the persistent relatively low the adoption rate of variable rate crop input application technology [@lowenberg2019setting]. Historically, site-specific yield response functions have been estimated using the data generated from strip trials conducted on only parts of fields [@makowski2001statistical; @scharf2002corn; @bullock2002adding; @mamo2003spatial; @hurley2004estimating; @anselin2004spatial; @scharf2005field; @ruffo2006site; @Miao2006; @puntel2019development].
But recently whole-field on-farm precision experimentation (OFPE) [@bullock2019] has allowed implementation of improved statistical experimental designs (e.g., Latin Square, Randomized Block) on entire fields [@laurent_kyveryga_makowski_miguez_2019; @licht_witt_2019]. Data generated from whole-field OFPEs typically have greater local variation in experimental input application rates and soil/field characteristics than do strip trial designs, which has improved the statistical identification of heterogeneous impacts of input management changes on yields. The resultant availability of more spatially detailed experiment data has encouraged a resurgence of interest in estimating site-specific yield response functions. For example, @barbosa2020modeling, @barbosa2020risk, @krause2020random and @Gardner21 used OFPE data to estimate site-specific yield response functions and economically optimal site-specific N fertilizer and/or seed rates. These recent studies used machine learning (ML) methods extensively in place of more traditional parametric modeling approaches. @barbosa2020modeling and @barbosa2020risk applied the Convolutional Neural Network approach, @krause2020random used Random Forest-based approaches, and @Gardner21 used the shape-constrained generalized additive model. 
But this trend of applying ML methods may raises concerns. Historically, agronomists have worked meticulously to develop clever experimental designs to identify causes of yield response to input management. But the aforementioned recent applications of ML methodologies pay little attention to identify such causes, instead attempting to validate their models by estimating yield prediction accuracy. But the ultimate goal of OFPE is the accurate prediction of EOIRs, not yields. These are distinct objectives, and achievement of one need not imply the other.

@@

Recent studies using ML methods to estimate the effectiveness of various agricultural input management strategies first estimate yield function, $f(I, \mathbf{c})$ (e.g., @barbosa2020modeling; @barbosa2020risk; @krause2020random; @Gardner21) and then derive changes in yield associated with changes in input rate to estimate site-specific input recommendations. On the other hand, Causal Forest is designed specifically to estimate a discrete version of Eq. \@ref(eq:eqn2) directly, examining the discrete changes in yield that result from discrete *changes* in the input application rate $I$, bypassing the estimation of $f(I, \mathbf{c})$. It may be suspected that CF will outperform other ML methods that identify EOIR indirectly through yield prediction. We now details how CF works below and why CF may perform better in predicting EOIR than other prediction-oriented ML methods used in the previous studies.

@@

The error term of the yield $\varepsilon$ represents the composite of all the unobserved factors that affect crop yield beyond $\alpha$, $\beta$, $ymax$ and $N$. Each cell $(i,j)$'s "true" optimal N application rate, denoted $N^{opt}_{i,j}$, was calculated by solving a profit maximization problem by cell assuming that the prices of corn and N fertilizer were $\$0.138/kg$ and $\$1.323/kg$, respectively. These prices are used consistently for our simulations. See Appendix C.1 for further details on how the parameters were generated and sample maps of the parameters and true economically optimal N rates.

@@

Unlike RF, BRF, and CNN, CF estimates the impact of a binary treatment. In our context, CF estimates changes in yields (i.e., $\hat{\tau}_{N^{con} \rightarrow N^{tre}}(\mathbf{\Omega_{i}})$) caused by changes in N application rates from one experimental rate (control N rate, i.e., $N^{con}$) to another experimental rate (treatment N rate, i.e., $N^{tre}$). Since we have five N application rates, four "experiments" (treatments) are identified based on four ($N^{con}$, $N^{tre}$) combinations. A possible grouping to make such pairwise N application rate combinations, which we call the "CF-base," used $(N_1, N_2),(N_1, N_3),(N_1, N_4)$, and $(N_1, N_5)$. In this approach, the treatment effect is always estimated against the lowest N rate ($N_1$) as $N^{con}$. The `grf` package (version 1.2.0 [@tibshirani2018package]) in R was used for CF estimation. Just like RF and BRF, hyperparameters were tuned using cross-validation.

@@

Interestingly, CNN completely failed in its estimations of site-specific EONRs. This happened because the site-specific yield response functions identified by CNN were linear, and all with the same slope. Therefore, CNN failed to capture a declining marginal product of N. The constant marginal product caused the estimated EONR to take on either the lowest or highest experimental N application rate. To examine whether this problem is a product solely of the specific choice of CNN architecture, we also tested another CNN model, which was analogous to CNN-ST proposed by @barbosa2020modeling. 
This architecture also estimated that yield and N rates were perfectly linearly related, and so estimated site-specific EONR poorly.

Note that @barbosa2020modeling just compared models through the lens of yield prediction but did not use the estimated models to derive EONRs. As an extensional work of @barbosa2020modeling, @barbosa2020risk used an ensemble of @barbosa2020modeling's CNN-LF models to estimate site-specific EOIR for N and seed based on the predicted yields. However, they did not evaluate how accuracy the EOIR estimates produced from their models. Again, this is simply infeasible in the real-world data because ground-truth EOIR are unobservable. Our simulation results suggest that CNN is inferior to RF, BRF and CF-base in estimating site-specific EONR.

@@

Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions. It plots the estimated treatment effects against true treatment effects by treatment type and ML method under the "aabbyytt" scenario in one of the one thousand simulation rounds. First of all, CNN suffers from severe underestimation of the impact of N in this particular simulation round. RF also suffers from underestimation of the impact of N. Underestimation of the impact of N generally leads to the underestimation of EONR, which in turn results in profit loss. Underestimation bias from BF is not as severe as RF or CNN. However, unlike RF, BRF, and CNN, points for CF-base clustered around the red 1-to-1 line, meaning that the estimated treatment effects from CF did not exhibit significant bias in treatment effect estimation. Moreover, points are clustered more tightly about the 1-to-1 line for CF-base than BRF. That is, CF-base estimated treatment effects more efficiently than did BRF.

@@

Finally, the simulation results at a smaller and larger size of the error term are presented in Appendix G as a sensitivity check for interested readers. Basically, qualitative results remain the same.

@@

Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations (see Figure \@ref(fig:vis-y-pred) in Appendix E for example visualizations of predicted and true yields along with RMSE values by model). Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN. Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact along with the poor performance of RF in predicting EONR presented in \@ref(tab:table-optN) show that strong predictive power of yield levels does not imply accurate prediction of EONR. Further, RF shows vulnerability to the inclusion of many correlated variables, as is displayed for EONR prediction as well. While CNN performed worse than RF and BRF in "aby" and "abytt," it performed better than RF in more complicated modeling scenarios, showing robustness, at least in yield prediction, to inclusion of many correlated variables. Of course, while on average in the "aabbyy" and "aabbyytt" scenarios CNN predicted yields better than RF did, CNN's EONR predictions were worse than RF's, which further backs our claim that a good yield prediction capability does not imply good EONR prediction capability.

@@

Figure \@ref(fig:vis-MB-BRF-y) illustrates the distinction between yield prediction at observed points and yield response function prediction, giving insights into why good yield prediction does not necessarily lead to good EONR prediction in general. The black curves are the true yield response functions for two sites in a single simulation round. Red symbols represent true (circle) or predicted (triangle) yields at the rate observed in the data: the rate that was actually applied in the experiment. That is, 150 kg/ha was applied to the two sites in the experiment. Blue symbols represent true (circle) or predicted (triangle) yield at some rates that were not observed (or applied) for the two sites in the experiment. Prediction-oriented ML methods train models to minimize errors in yield level prediction at the "observed" rates (red points). Both RF- and BRF-trained models predict yield level at the observed rate well for the two sites (the vertical distance between the red circle and triangle). However, as you move away from the observed N rate, yield prediction errors tend to become larger (of course smaller yield prediction errors can be observed at unobserved rates some times). More important, connecting the predicted yield points does not trace the true yield response curves well for both RF and BRF. Specifically, in this example, the predicted impact of N on yield from RF and BRF are both smaller than the true impact of N.

@@

In essence, Figure \@ref(fig:vis-MB-BRF-y) illustrates that good performance in predicting yield "levels" at the "observed" points does not mean good performance in predicting yield "response" function, which is about finding out what "would" happen to yield if rates other than the one actually applied were applied. This happens because you can predict yield "levels" for wrong reasons by giving wrong amount of credit to wrong drivers (variables) of yield levels. The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary objective of predicting yield levels well at the "observed" nitrogen rate for each site well. This problem is also observable at Figure \@ref(fig:plot-tre), which shows both RF and BRF underestimates the impact of N on yield: or in other words, their predicted site-specific yield response functions tend to be flatter than they truly are. Of course, the CNN approach in our study is an extreme case where it completely fails to recognize the contribution of N on yield. But, remember that CNN does performs almost as good as RF and BRF in yield prediction as shown in Table \@ref(tab:table-y).

Since you need to be able to estimate yield curves (yield response function) well at the site level to predict site-specific EONR (not yield level) well, models' ability to predict yield levels well at the observed rates does not guarantee their ability to predict site-specific EONR well. In contrast to RF, BRF, and CNN, CF focuses to recover the yield response functions well (or alternatively the causal impact of N on yield at different discrete rates of N). We showed that CF can predict the impact of N on yield when N is changed from an unobserved rate to another unobserved rats as shown in Figure \@ref(fig:plot-tre), which then translated to better performance in predicting EONR and profit.

All previous research has followed a two-step procedure to estimate site-specific EONRs. The first step was to select the model that predicts yield levels most accurately at the observed points, and the following step used the selected model to predict EONR. As discussed earlier, this practice can be economically harmful. Figure \@ref(fig:vis-RMSE-y-eonr) further illustrates the underlying problem. It plots RMSE of yield (x-axis) and EONR (y-axis) predictions by model and simulation round for several simulation rounds. As you can see clearly, the model with the lowest yield RMSE is not necessarily the model with the lower EONR RMSE for a given simulation round (simulation round 20 and 30).

```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "The Relationship between yield and EONR Prediction Performances under the aabbyytt scenario"}
vis_RMSE_y_eonr
```

@@

We examined the use of CF in the generation of site-specific input management recommendations. Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN. CF consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation. Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF. It is important to keep in mind that we are not claiming that CF always performs better economically than RF, BRF, and CNN. Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research.
